### 2019-08-15 reports/thesis/chapters/3_compoundPoisson.tex
Update bib

In an x-ray tube, photons are emitted as a Poisson process and each photon has some random energy due to bremsstrahlung and characteristic radiation. This shares similarities to the compound Poisson. Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$. Each photon is assumed to be i.i.d.~with energy $U_i$ for $i=1,2,3,\dotsc$. $U_i$ has p.d.f.~$p_U(u)$. The random variables discussed here covers all the latent variables in the compound Poisson.

>>>>

In an x-ray tube, photons are emitted as a Poisson process \citep{cierniak2011x} and each photon has some random energy due to bremsstrahlung and characteristic radiation \citep{sun2012overview}. This shares similarities to the compound Poisson. Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$. Each photon is assumed to be i.i.d.~with energy $U_i$ for $i=1,2,3,\dotsc$. $U_i$ has p.d.f.~$p_U(u)$. The random variables discussed here covers all the latent variables in the compound Poisson.
